Decentralised Authoring, Annotations and Notifications for a Read-Write Web with dokieli

### 2017-04-07 index.tex
consistent spelling

                                \textit{Pundit} is a set of tools that allow web annotation with highlights, comments and semantic annotations. It is similar to hypothes.is in its architecture and deployment, i.e., annotations made through the pundit client require it to be saved on its corresponding annotations server.

>>>>

                                \textit{Pundit} is a set of tools that allow web annotation with highlights, comments and semantic annotations. It is similar to Hypothesis in its architecture and deployment, i.e., annotations made through the pundit client require it to be saved on its corresponding annotations server.
